
\begin{thebibliography}{1} 
    
   \bibitem{1}
   C. Gomes, C. Thule, P.G. Larsen, J. Denil, H. Vangheluwe, Co-simulation of continuous systems: a tutorial, 2018, arXiv preprint arXiv:1809.08463

  \bibitem{2}
    C. Thule, C. Gomes, J. Deantoni, P.G. Larsen, J. Brauer, H. Vangheluwe, Towards the verification of hybrid co-simulation algorithms, in: Federation of
International Conferences on Software Technologies: Applications and Foundations, Springer, 2018, pp. 5–20.
  \bibitem{b1} Andreas Abel, Torsten Blochwitz, Alexander Eichberger, Peter Hamann, and Udo Rein. Functional mock-up interface in mechatronic gearshift simulation for commercial vehicles. In 9th International Modelica Conference. Munich, 2012.
  
  \bibitem{b2} D. Bian, M. Kuzlu, M. Pipattanasomporn, S. Rahman, and Y. Wu. Real-time co-simulation platform using OPAL-RT and OPNET for analyzing smart grid performance. In 2015 IEEE Power \& Energy Society General Meeting, pages 1–5. IEEE, jul 2015. ISBN 978-1-4673-8040-9.
  
  \bibitem{b3} John Fitzgerald, Carl Gamble, Richard Payne, Peter Gorm Larsen, Stylianos Basagiannis, and Alie El-Din Mady. Collaborative Model-based Systems Engineering for Cyber-Physical Systems – a Case Study in Building Automation. In INCOSE 2016, Edinburgh, Scotland, jul 2016.
  
  \bibitem{b4} Nicolai Pedersen, Jan Madsen, and Morten Vejlgaard-Laursen. Co-Simulation of Distributed Engine Control System and Network Model using FMI \& SCNSL. IFAC-PapersOnLine, 48 (16):261–266, 2015. ISSN 24058963.
  
  \bibitem{b5} Michal Kudelski, Luca M. Gambardella, and Gianni A. Di Caro. RoboNetSim: An integrated framework for multi-robot and network simulation. Robotics and Autonomous Systems, 61 (5):483–496, may 2013. ISSN 09218890.
  
  \bibitem{b6} The leading standard to exchange dynamic simulation models. Functional Mock-up Interface. (n.d.). \url{https://fmi-standard.org/ }
  \bibitem{b7} Cláudio Gomes, Casper Thule, David Broman, Peter Gorm Larsen and Hans Vangheluwe. Co-simulation: State of the art, 2017; arXiv:1702.00686.
  \bibitem{b8}Martin Arnold and Michael Gunther. Preconditioned Dynamic Iteration for Coupled Differential-Algebraic Systems. BIT Numerical Mathematics, 41(1):1–25, 2001. doi: 10.1023/ A:1021909032551.
  \bibitem{b9}B. Schweizer and D. Lu. Predictor/corrector co-simulation approaches for solver coupling with algebraic constraints. ZAMM - Journal of Applied Mathematics and Mechanics, 95(9):911–938, sep 2015. ISSN 00442267. doi: 10.1002/zamm.201300191.
  \bibitem{b10} Bei Gu and H H Asada. Co-simulation of algebraically coupled dynamic subsystems. In American Control Conference, 2001. Proceedings of the 2001, volume 3, pages 2273–2278 vol.3, 2001. ISBN 0743-1619 VO - 3. doi: 10.1109/ACC.2001.946089.
  \bibitem{b11} Adelinde M. Uhrmacher. Variable structure models: autonomy and control answers from two different modeling approaches. In 4th Annual Conference on AI, Simulation and Planning in High Autonomy Systems, pages 133–139. IEEE Comput. Soc. Press, 1993. ISBN 0-8186-40200. doi: 10.1109/AIHAS.1993.410588.
  \bibitem{b12}R. Kübler and W. Schiehlen. Two Methods of Simulator Coupling. Mathematical and Computer Modelling of Dynamical Systems, 6(2):93–113, jun 2000. ISSN 1387-3954. doi: 10.1076/1387-3954(200006)6:2;1-M;FT093.
  \bibitem{b13}Simon Thrane Hansen, Casper Thule, Cláudio Gomes, Kenneth Guldbrandt Lausdahl, Frederik Palludan Madsen, Giuseppe Abbiati, Peter Gorm Larsen,
  Co-simulation at different levels of expertise with Maestro2,
  Journal of Systems and Software,Volume 209,2024,111905,ISSN 0164-1212,
  https://doi.org/10.1016/j.jss.2023.111905.
  \bibitem{b14}Ochel, L., Braun, R., Thiele, B., Asghar, A., Buffoni, L., Eek, M., Fritzson, P., Fritzson, D., Horkeby, S., Hällquist, R., Kinnander, Å., Palanisamy, A., Pop, A., \& Sjölund, M. (2019). Omsimulator - integrated FMI and TLM-based co-simulation with composite model editing and SSP. Linköping Electronic Conference Proceedings. https://doi.org/10.3384/ecp1915769 
  \bibitem{b15}Évora Gómez, J., Hernández Cabrera, J. J., Tavella, J.-P., Vialle, S., Kremers, E., \& Frayssinet, L. (2019). Daccosim ng: Co-simulation made simpler and faster. Linköping Electronic Conference Proceedings. https://doi.org/10.3384/ecp19157785
  \bibitem{b16}Andersson, C., Åkesson, J., \& Führer, C. (2016). PyFMI: A Python Package for Simulation of Coupled Dynamic Models with the Functional Mock-up Interface. (Technical Report in Mathematical Sciences; Vol. 2016, No. 2). Centre for Mathematical Sciences, Lund University.
  \bibitem{17}
  Dempsey, M. (2006). Dymola for multi-engineering modelling and Simulation. 2006 IEEE Vehicle Power and Propulsion Conference. \url{https://doi.org/10.1109/vppc.2006.364294 }

  \bibitem{b17}Vanfretti, L., Baudette, M., Amazouz, A., Bogodorova, T., Rabuzin, T., Lavenius, J., \& Goméz-López, F. J. (2016). Rapid: A modular and extensible toolbox for parameter estimation of Modelica and FMI compliant models. SoftwareX, 5, 144–149. https://doi.org/10.1016/j.softx.2016.07.004 
  \bibitem{18}
  Perabo, F., Park, D., Zadeh, M. K., Smogeli, O., \& Jamt, L. (2020). Digital twin modelling of ship power and propulsion systems: Application of the open simulation platform (OSP). 2020 IEEE 29th International Symposium on Industrial Electronics (ISIE).\url{https://doi.org/10.1109/isie45063.2020.9152218 }
  \bibitem{b18}Arnold, M., Clauß, C., Schierz, T.: Error analysis and error estimates for cosimulation in FMI for model exchange and co-simulation v2.0. In: Sch¨ops, S., Bartel, A., G¨unther, M., ter Maten, E.J.W., M¨uller, P.C. (eds.) Progress in DifferentialAlgebraic Equations. DEF, pp. 107–125. Springer, Heidelberg (2014). https://doi.org/10.1007/978-3-662-44926-4\_6
  \bibitem{b19}Hansen, S. T., Thule, C., \& Gomes, C. (2021). An FMI-Based Initialization Plugin for INTO-CPS Maestro 2. In L. Cleophas, \& M. Massink (Eds.), Software Engineering and Formal Methods: SEFM 2020 Collocated Workshops (pp. 295-310). Springer. https://doi.org/10.1007/978-3-030-67220-1\_22
  \bibitem{b21}
  Alfredo Garro and Alberto Falcone. On the integration of HLA and FMI for supporting interoperability and reusability in distributed simulation. In Spring Simulation Multi-Conference, pages 774–781. Society for Computer Simulation International, 2015.
  \bibitem{b22}
  Tavella JP., Caujolle M., Tan M.,Plessis G., Schumann M., Vialle S., Dad C., et al. Toward an Hybrid Co-simulation with the FMI-CS Standard, apr 2016. \url{ https://hal-centralesupelec.archives-ouvertes.fr/hal-01301183}.
  \bibitem{b23}
  Jean-Sebastien Bolduc and Hans Vangheluwe. Mapping odes to devs: Adaptive quantization. In Summer Computer Simulation Conference, pages 401–407. Society for Computer Simulation International; 1998, 2003. ISBN 0094-7474.
  \bibitem{b24}
  Q. Alfalouji et al., « Co-simulation for buildings and smart energy systems — A taxonomic review », Simul. Model. Pract. Theory, vol. 126, p. 102770, juill. 2023, doi: \url{10.1016/j.simpat.2023.102770.}
  \bibitem{b25}
  N. Guarino et C. Welty, « Ontological Analysis of Taxonomic Relationships », in Conceptual Modeling — ER 2000, A. H. F. Laender, S. W. Liddle, et V. C. Storey, Éd., Berlin, Heidelberg: Springer, 2000, p. 210‑224. doi: \url{10.1007/3-540-45393-8_16}.
  \bibitem{b26}
  D. Krob, « Éléments de systémique. Architecture des systèmes », in Complexité-Simplexité, A. Berthoz et J.-L. Petit, Éd., Collège de France, 2014. doi: \url{10.4000/books.cdf.3388}.
  \bibitem{26}
Hatledal, L. I., Zhang, H., \& Collonval, F. (2020). Enabling python driven co-simulation models with Pythonfmu. ECMS 2020 Proceedings Edited by Mike Steglich, Christian Mueller, Gaby Neumann, Mathias Walther. \url{https://doi.org/10.7148/2020-0235 }
\bibitem{27}
Legaard, C., Tola, D., Schranz, T., Macedo, H., \& Larsen, P. (2021). A universal mechanism for implementing functional mock-up units. Proceedings of the 11th International Conference on Simulation and Modeling Methodologies, Technologies and Applications. \url{https://doi.org/10.5220/0010577601210129 }
  \bibitem{b27}
  Héléna Shourick, Damien Tromeur-Dervout and Laurent Chédot. Co-simulation domain decomposition algorithm for hybrid EMT-Dynamic Phasor modeling, 2022; arXiv:2212.05232.

\bibitem{b28}
Garbey, M., \& Tromeur‐Dervout, D. (2002). On some aitken‐like acceleration of the Schwarz method. International Journal for Numerical Methods in Fluids, 40(12), 1493–1513. \url{https://doi.org/10.1002/fld.407 }
\bibitem{29}
Eguillon, Y., Lacabanne, B., Tromeur-Dervout, D.: IFOSMONDI: A Generic Co-simulation Approach Combining Iterative Methods for Coupling Constraints and
Polynomial Interpolation for Interfaces Smoothness. In: 9th International Conference on Simulation and Modeling Methodologies, Technologies and Applications.
pp. 176–186. SCITEPRESS - Science and Technology Publications, Prague, Czech
Republic (Jul 2019),\url{ https://doi.org/10.5220/0007977701760186}
\bibitem{30}
Busch, M.: Performance Improvement of Explicit Co-simulation Methods
Through Continuous Extrapolation. In: IUTAM Symposium on solver-coupling
and co-simulation. IUTAM Bookseries, vol. 35, pp. 57–80. IUTAM (2019).
\url{https://doi.org/10.1007/978-3-030-14883-6}
\bibitem{31}
Eguillon Y.,Lacabanne B. and Tromeur-Dervout D.. COSTARICA estimator for rollback-less systems handling in iterative co-simulation algorithms, 2022; arXiv:2203.11752.
\end{thebibliography}